Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-12 programlogic.tex
+
some edits and comments and todos for myself on section 4

@@

\begin{figure*}
 Definition $\pfpointsto\locsf\vpts\qfrac\ppts$ :vProp $\Sigma$ := pmapsto_def_v (pfn w) (page_off w) q v.
 Definition $\vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\vpage$ :vProp $\Sigma$ := 
  $\exists_{\textsf{l4e l3e l2e l1}} \ldotp$  $\ulcorner$ aligned $\vaddr \urcorner \ast$ L4_L1_PointsTo(rtv maddr l4e l3e l2e l1e) $\ast$ addr_L1$(\vaddr,\textsf{l1e}) \mapsto_{p} \vpage$.
 Definition L4_L1_PointsTo (rtv maddr l4e l3e l2e l1e :word 64) : vProp $\Sigma$ :=
  (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} l4e  $\ast$
  (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e $\ast$ 
  (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e) $\mapsto_{a}$ {q3} l2e $\ast$
  (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e) $\mapsto_{a}$ {q4} l1e.
\caption{A Strong Virtual Points-to Relation}
\todo[inline,color=red]{Colin says: shouldn't that fraction be a q, not a 1, in the second line?}
  \label{fig:strongvirtualpointsto}
\end{figure*}
Given the definition of physical page-pointsto assertion and the root address of virtual-address space as shown in Figure \ref{fig:pagetable}, one can build the physical address-translation for a virtual address (e.g. \textsf{va}) via abstracting the L4-L1 table traversal as the following:
\begin{itemize}
  \item Level-4 Translation (L4): Performs the first level address translation to get the L4 entry (L4E) in Figure \ref{fig:pagetables} by using the masks l4M52 and l4off with \textsf{rtv} virtual base address to get the starting address of the L4 table (L4T), and locate the entry entry amongst 512 (q1) respectively.
      $\hbox{(\TirNameStyle{{L4translate}})} \quad$ (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} l4e 
 \item Level-3 Translation (L3): Performs the second level address translation to get the L3 entry (L3E) in Figure \ref{fig:pagetables} by using the masks l3M52 and l3off with L4 entry (l4e) to get the starting address of the L3 table (L3T), and locate the entry amongst 512 (q2) respectively.
    $\hbox{(\TirNameStyle{{L3translate}})}$ (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e
  \item Level-2 Translation (L2): Performs the second level address translation to get the L2 entry (L2E) in Figure \ref{fig:pagetables} by using the masks l2M52 and l2off with L3 entry (l3e) to get the starting address of the L2 table (L2T), and locate the entry entry amongst 512 (q3) respectively.
    $\hbox{(\TirNameStyle{{L2translate}})}$ (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e)  $\mapsto_{a}$ {q3} l2e
  \item Level-1 Translation (L1): Performs the second level address translation to get the L1 entry (L1E) in Figure \ref{fig:pagetables} by using the masks l1M52 and l1off with L2 entry (l2e) to get the starting address of the L1 table (L1T), and locate the entry entry amongst 512 (q4) respectively.
    $\hbox{(\TirNameStyle{{L1translate}})}$ (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e)  $\mapsto_{a}$ {q4} l1e
  \item Page Address Level Translation: Final computed physical page-address ($\textsf{addr\_L1}(\vaddr$,$\textsf{l1e}$)) points-to the value stored in the address ($\vpage$).
    $\hbox{(\TirNameStyle{{PageLabelAccess}})} \qquad$ addr_L1($\vaddr,\textsf{l1e}$) $\mapsto_{p} \vpage$.
\end{itemize}
\subsection{An Overly-Restrictive Definition for Virtual Memory Addressing}
One could give a naive logical definition to the virtual mememory addressing as conjuctions of each level translation 
(Figure \fref{fig:strongvirtualpointsto}). The very first assurance our logical constructions need to be able assert is 
the \textit{existence} of the page table walk. Our naive attempt shown in Figure \ref{figure:strongvirtualpointsto}, 
we see that a virtual address with a certain fractional permissions at each level of the page-table walk gives us sound 
assurance of the path existence reaching to a page table entry, consequently, with a full-ownership of page address, 
we can obtain and update the value mapped value at this physical page address through our virtual memory address.

\todo[inline]{Cite Kolanski here; not all of them, but some actually defined it exactly this way, for the current
address space.}
\subsection{Aliasing/Sharing Physical Pages}
  \label{sec:sharingpages}  
  One might have already observed that the virtual points-to definition shown in Figure \ref{fig:strongvirtualpointsto} 
  is too strong to specify some operations updating a page table entry.
   To speak more concretely, the fractional permissions on the page-table-walk assertion ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ in Figure \ref{fig:strongvirtualpointsto}) 
  ensure fractional ownership of the four physical page table entries accessed by the hardware during address translation,
  as well as the physical memory holding the data of the virtual points-to.
  However, this formulation stores knowledge of the page table walk's details with ownership of the backing physical
  memory.
  Updating any of these mappings (e.g., move the page tables in physical memory, as in coallescing for
  superpages or hugepages)
  would require explicitly collecting all virtual points-to facts that traverse affected entries.
  It is preferable to permit the page tables themselves to be updated independently of the virtual points-to assertions,
  so long as those updates preserve the same virtual-to-physical translations.

\begin{figure*}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v,rtv}}\{\textsf{q}\}\vpage \stackrel{\triangle}{:=} 
    \exists \paddr\ldotp
    \sumapaces\rtv\delta \ast 
  \sumwalkabs\vaddr\qfrac\paddr \ast \paddr \mapsto_{p} \vpage
\end{array}
\]
\caption{Virtual-Pointsto for Sharing Pages}
  \label{fig:virtualpointstosharing}
\end{figure*}  
  One possible approach is to abstract away the physical page-table-walk pointsto ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ in Figure \ref{fig:strongvirtualpointsto}) from the virtual pointsto relation. To do so, we introduce the protocol separating read-only (fragmental) and authorative (full ownership) accesses to the page tables, specifically $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$. We realize this protocol by embedding it into an already existing \textsf{Iris}'s ghost-map (or view\_maps) construction
  \[\mathcal{A}\textsf{bsPTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  (\mathcal{W}_{64} \; \rightarrow_{\textrm{fin}}\;  (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
 where
  \begin{itemize}
  \item we decorate the fragmental ownership of the ghost-map ($ \sumwalkabs\vaddr\qfrac\paddr$) with the physical $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ whose ownership just ensures that the virtual address ($\vaddr$) is mapped to a page (referenced by $\paddr$)
  \item we place the authorative ownership $\mathcal{A}\textsf{PTableWalk}$ of the ghost-map in an address-space invariant ($\mathcal{I}$\textsf{ASpace} in Figure \ref{fig:peraspaceinvariant}) whose ownership grants sound update on the page table entries
  \end{itemize}

@@

\begin{remark}[Exchanging Page-Table-Walk-Summarization Mappings (Tokens) under Mutation of Page Tables ]
  $\mathcal{A}\textsf{PTableWalk}$'s fragmental-ownership represents an individual key-value pair (per-virtual-address) which can be handled as a \textit{look-up} resource for an individual virtual address.
  To build more intuition on the convenience of this protocol, we can think of the use-case \textit{unmapping-pages}. Normally, in the existence of shared page-tables, we need to first collect all the fragmental map pairs, e.g. $\sumwalkabs\vaddr\qfrac\paddr$, then, after making sure of non-existence of \textit{sharing}, we can \textit{unmap} the page. In this case, it would be ok to put $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ and $ \sumwalkabs\vaddr\qfrac\paddr$ side-by-side inside the virtual-pointsto definition in Figure \ref{fig:virtualpointstosharing}. However, this pattern of verifying is not only inconvenient due to requirement of extra bookkeeping, but also violates our soundness argument based on considering  mutation on the shared page-tables -- due to coalescing of page tables etc. --. In other words, physical $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ sitting aside to  $ \sumwalkabs\vaddr\qfrac\paddr$ would be made invalid by any concurrent update on the physical page-table. So there should only be one physical memory resource inside the virtual pointsto definition: from physical page address to the value stored ($ \paddr \mapsto_{p} \vpage$).
\end{remark}

@@

\subsection{Address-Space Management}
\label{sec:aspacemanagement}
So far, we have introduced logical abstractions for a single address space. However, \textsf{VMM} implementations handle more than one address-space which we abstract as a ghost map from root address of an address-space to a namespace labelling the address space
\[\mathcal{A}\textsf{spaces} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \; (\textsc{Agree } \mathsf{GName},\mathord{=}) ) \]

>>>>

\todo[inline,color=red]{Colin says: This syntax is what most readers would expect for physical poinst-tos, but it's
inconsistent with the split 52+12  stuff later... Whatever we do, we need to be consistent}

@@

\begin{figure*}
  \begin{lstlisting}[language=Coq]
 Definition $\pfpointsto\locsf\vpts\qfrac\ppts$ :vProp $\Sigma$ := pmapsto_def_v (pfn w) (page_off w) q v.
 Definition $\vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\vpage$ :vProp $\Sigma$ := 
  $\exists_{\textsf{l4e l3e l2e l1}} \ldotp$  $\ulcorner$ aligned $\vaddr \urcorner \ast$ L4_L1_PointsTo(rtv maddr l4e l3e l2e l1e) $\ast$ addr_L1$(\vaddr,\textsf{l1e}) \mapsto_{p} \vpage$.
 Definition L4_L1_PointsTo (rtv maddr l4e l3e l2e l1e :word 64) : vProp $\Sigma$ :=
  (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} l4e  $\ast$
  (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e $\ast$ 
  (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e) $\mapsto_{a}$ {q3} l2e $\ast$
  (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e) $\mapsto_{a}$ {q4} l1e.
\end{lstlisting}
\caption{A Strong Virtual Points-to Relation}
\todo[inline,color=red]{Colin says: shouldn't ther be a fraction q in the body of the virtual pointsto def?
I know this is just a sketch that we then move away from, but it's worth getting accurate.}
\todo[inline,color=cyan]{Colin says: the virtual points-to here is not defined as a vprop! the body is an iProp,
containing an unbound variable rtv, which should be the cr3val taken as an argument. (Also, rtv doesn't make sense to me
as a shorthand, why not cr3val?). I'm also pretty sure the maddr in the virtual points-to definition should be va.}
  \label{fig:strongvirtualpointsto}
\end{figure*}

\todo[inline,color=red]{Colin says: Ismail, I think you accidentally deleted discussion of physical points-tos here?}

\todo[inline,color=red]{Colin says: Why are we talking about assertions for address translations here? It seems like we should
\todo[inelin]{Colin says: There's no explanation of the split 52+12 \emph{notation} here. If we added such an explanation
(maybe to where physical points-tos are introduced?) and moved this discussion to \ref{sec:overly-restrictive}, this is otherwise
a nice explanation}
discuss physical memory pointsto assertions in general first, then talk about this in \ref{sec:overly-restrictive}}
Given the definition of physical page-pointsto assertion and the root address of virtual-address space as shown in Figure \ref{fig:pagetable}, one can build the physical address-translation for a virtual address (e.g. \textsf{va}) via abstracting the L4-L1 table traversal as the following:
\begin{itemize}
  \item Level-4 Translation (L4): Performs the first level address translation to get the L4 entry (L4E) in Figure \ref{fig:pagetables} by using the masks l4M52 and l4off with \textsf{rtv} virtual base address to get the starting address of the L4 table (L4T), and locate the entry entry amongst 512 (q1) respectively.
    \begin{lstlisting}[language=Coq]
      $\hbox{(\TirNameStyle{{L4translate}})} \quad$ (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} l4e 
    \end{lstlisting}
 \item Level-3 Translation (L3): Performs the second level address translation to get the L3 entry (L3E) in Figure \ref{fig:pagetables} by using the masks l3M52 and l3off with L4 entry (l4e) to get the starting address of the L3 table (L3T), and locate the entry amongst 512 (q2) respectively.
    \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L3translate}})}$ (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e
    \end{lstlisting}
  \item Level-2 Translation (L2): Performs the second level address translation to get the L2 entry (L2E) in Figure \ref{fig:pagetables} by using the masks l2M52 and l2off with L3 entry (l3e) to get the starting address of the L2 table (L2T), and locate the entry entry amongst 512 (q3) respectively.
\begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L2translate}})}$ (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e)  $\mapsto_{a}$ {q3} l2e
    \end{lstlisting}
  \item Level-1 Translation (L1): Performs the second level address translation to get the L1 entry (L1E) in Figure \ref{fig:pagetables} by using the masks l1M52 and l1off with L2 entry (l2e) to get the starting address of the L1 table (L1T), and locate the entry entry amongst 512 (q4) respectively.
   \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L1translate}})}$ (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e)  $\mapsto_{a}$ {q4} l1e
    \end{lstlisting}
  \item Page Address Level Translation: Final computed physical page-address ($\textsf{addr\_L1}(\vaddr$,$\textsf{l1e}$)) points-to the value stored in the address ($\vpage$).
   \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{PageLabelAccess}})} \qquad$ addr_L1($\vaddr,\textsf{l1e}$) $\mapsto_{p} \vpage$.
    \end{lstlisting} 
\end{itemize}

\subsection{An Overly-Restrictive Definition for Virtual Memory Addressing}
\label{sec:overly-restrictive}
One could give a naive logical definition to the virtual mememory addressing as conjuctions of each level translation 
(Figure \fref{fig:strongvirtualpointsto}). The very first assurance our logical constructions need to be able assert is 
the \textit{existence} of the page table walk. Our naive attempt shown in Figure \ref{figure:strongvirtualpointsto}, 
we see that a virtual address with a certain fractional permissions at each level of the page-table walk gives us sound 
assurance of the path existence reaching to a page table entry, consequently, with a full-ownership of page address, 
we can obtain and update the value mapped value at this physical page address through our virtual memory address.

\todo[inline]{Cite Kolanski here; not all of them, but some actually defined it exactly this way, for the current
address space.}
\subsection{Aliasing/Sharing Physical Pages}
  \label{sec:sharingpages}  
  One might have already observed that the virtual points-to definition shown in Figure \ref{fig:strongvirtualpointsto} 
  is too strong to specify some operations a virtual memory manager may need to do, such as
  move one level of the page table to a different physical location while preserving all virtual-to-physical mappings.\footnote{
    x86-64 hardware, like other architectures, includes a feature (which we do not formalize assertions for) to
    replace an L1 page table address in an L2 entry with a pointer to a \emph{larger} 2MB page (called super-pages), 
    or replace an L2 page table address in an L3 entry with a pointer to a 1GB page (called huge-pages).
  }
   To speak more concretely, the fractional permissions on the page-table-walk assertion ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ in Figure \ref{fig:strongvirtualpointsto}) 
  ensure fractional ownership of the four physical page table entries accessed by the hardware during address translation,
  as well as the physical memory holding the data of the virtual points-to.
  However, this formulation stores knowledge of the page table walk's details with ownership of the backing physical
  memory.
  Updating any of these mappings (e.g., move the page tables in physical memory, as in coallescing for
  superpages or hugepages)
  would require explicitly collecting all virtual points-to facts that traverse affected entries.
  It is preferable to permit the page tables themselves to be updated independently of the virtual points-to assertions,
  so long as those updates preserve the same virtual-to-physical translations.

\begin{figure*}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v,rtv}}\{\textsf{q}\}\vpage \stackrel{\triangle}{=} 
    \exists \paddr\ldotp
    \sumapaces\rtv\delta \ast 
  \sumwalkabs\vaddr\qfrac\paddr \ast \paddr \mapsto_{p} \vpage
\end{array}
\]
\todo[inline]{Colin says: again, this is supposed to be a vprop, but isn't doing anything with a cr3val argument.
I realize the GASI and per-address-space invariants, and therefore machinery to tie the virtual points-to
to the GASI, hasn't been introduced yet. Is there a short-hand here we can use to be ``more complete'' until the later text
that fills in these details?
}
\todo[inline,color=cyan]{Colin says: Oh!!! I see. You have that extremely subtle rtv subscript on the virtual points-to
syntax! Don't do that. First, it's really subtle and wasn't explained anywhere, so even I missed it. Second,
we're very explicitly describing vProps as functions from root to iProp. Sticking the rtv on the arrow there
is partly weird because it obscures which argument is really the vProp argument (there are 2 other word64s in that syntax),
partly weird because it's written next to something that \emph{isn't} a variable (the v subscript on the virtual points-to
arrow) while using the same font, and partly weird because when you actually write these assertions, rtv doesn't show
up in the syntax at all, which is the whole point --- virtual points-to defs shouldn't mention their cr3 or address space at
all!
Here's what I think it should look like (I also existentially quantified $\delta$ and fixed the p subscript on physical
points-to):
}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage : \mathsf{vProp}~\Sigma \stackrel{\triangle}{=} 
    \lambda \mathit{cr3val}\ldotp
    \exists \paddr\ldotp
    \exists \delta\ldotp
    \sumapaces{\mathit{cr3val}}\delta \ast 
  \sumwalkabs\vaddr\qfrac\paddr \ast \paddr \mapsto_{\mathsf{p}} \vpage
\end{array}
\]
\todo[inline]{Colin says: The fact that we can't visually distinguish the variable v that is the value in memory
from the subscript v on the virtual points-to arrow is not ideal: it makes it hard to tell what's concrete syntax
and what's a variable. This is worth fixing, but near the bottom of the priority list}
\caption{Virtual-Pointsto for Sharing Pages}
  \label{fig:virtualpointstosharing}
\end{figure*}

  Intuitively, the definition in Figure \ref{fig:strongvirtualpointsto} is too strong because the virtual points-to
  assertion there tracks too much information: when writing programs that access memory via virtual addresses,
  most code does not care \emph{which physical memory locations are involved in address translation}: it only cares
  that virtual address translation would succeed. The necessary information about the physical page table walk
  must still be tracked, but can be tracked separately from the virtual points-to assertion itself.

  We take the approach of separating the physical page-table-walk pointsto ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ in Figure \ref{fig:strongvirtualpointsto}) 
  from the virtual pointsto relation. 
  To do so, we take advantage of an Iris construction which permits tracking a map in ghost state that maps
  virtual addresses to the physical addresses they translate to, and has for each key in the map (i.e.,
  each virtual address) a token. Updating the virtual-to-physical (ghost) mapping for a virtual address $va$
  requires full ownership of the token. In addition, we keep an invariant that for each $va\mapsto pa$ mapping
  in this map, there are \emph{physical} resources sufficient to ensure that address translation for $va$
  will resolve in the hardware to $pa$. But these physical resources, which specify \emph{which} physical locations
  are involved in the page table walk, are now separated from but consistent with
  the knowledge that such resources exist (which is embodied by the token for $va$, which tracks that $va$ maps to $pa$
  in the ghost map). Thus we can store the token which summarizes the translation and ensures it exists in the virtual
  points-to, and keep the ghost map and the invariant that every mapping in the ghost map has corresponding physical resources
  for translation in a separate global invariant.

  \todo[inline]{Colin says: This requires explaining all the math here. Most reviewers of our paper will not be Iris
  experts. Even the notion of an authoritative RA is something you'd need to explain (the general idea of).
  So: write for non-Iris-expert readers. Above I explained the intuition behind the construction, so now we have to show
  that we correctly implemented that intuition in Iris. So explain authoritative RAs, and how the line below
  implements the intuition above.}
  To do so, we introduce the protocol separating read-only (fragmental) and authorative (full ownership) accesses to the page tables, specifically $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$. We realize this protocol by embedding it into an already existing \textsf{Iris}'s ghost-map (or view\_maps) construction
  \[\mathcal{A}\textsf{bsPTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  (\mathcal{W}_{64} \; \rightarrow_{\textrm{fin}}\;  (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
 where
  \begin{itemize}
  \item we decorate the fragmental ownership of the ghost-map ($ \sumwalkabs\vaddr\qfrac\paddr$) with the physical $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ whose ownership just ensures that the virtual address ($\vaddr$) is mapped to a page (referenced by $\paddr$)
  \item we place the authorative ownership $\mathcal{A}\textsf{PTableWalk}$ of the ghost-map in an address-space invariant ($\mathcal{I}$\textsf{ASpace} in Figure \ref{fig:peraspaceinvariant}) whose ownership grants sound update on the page table entries
  \end{itemize}

@@

\todo[inline]{Colin says: I can rewrite this remark into flowing text after you fully explain the math above.}
\begin{remark}[Exchanging Page-Table-Walk-Summarization Mappings (Tokens) under Mutation of Page Tables ]
  $\mathcal{A}\textsf{PTableWalk}$'s fragmental-ownership represents an individual key-value pair (per-virtual-address) which can be handled as a \textit{look-up} resource for an individual virtual address.
  To build more intuition on the convenience of this protocol, we can think of the use-case \textit{unmapping-pages}. Normally, in the existence of shared page-tables, we need to first collect all the fragmental map pairs, e.g. $\sumwalkabs\vaddr\qfrac\paddr$, then, after making sure of non-existence of \textit{sharing}, we can \textit{unmap} the page. In this case, it would be ok to put $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ and $ \sumwalkabs\vaddr\qfrac\paddr$ side-by-side inside the virtual-pointsto definition in Figure \ref{fig:virtualpointstosharing}. However, this pattern of verifying is not only inconvenient due to requirement of extra bookkeeping, but also violates our soundness argument based on considering  mutation on the shared page-tables -- due to coalescing of page tables etc. --. In other words, physical $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ sitting aside to  $ \sumwalkabs\vaddr\qfrac\paddr$ would be made invalid by any concurrent update on the physical page-table. So there should only be one physical memory resource inside the virtual pointsto definition: from physical page address to the value stored ($ \paddr \mapsto_{p} \vpage$).
\end{remark}

@@

\subsection{Address-Space Management}
\label{sec:aspacemanagement}
\todo[inline]{Colin says: I will go back and add some foreshadowing in the explanation of virtual points-to,
which already contains the Aspaces lookup a couple pages back.}
So far, we have introduced logical abstractions for a single address space. However, \textsf{VMM} implementations handle more than one address-space which we abstract as a ghost map from root address of an address-space to a namespace labelling the address space
\[\mathcal{A}\textsf{spaces} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \; (\textsc{Agree } \mathsf{GName},\mathord{=}) ) \]
